Convex Surrogates via Polyhedral Losses

### 2019-05-02 notes/bo-separated.tex
old changes

\begin{lemma} \label{lemma:U-close-intersect}
  Let $\epsilon$ be given by Lemma \ref{lemma:conv-R-min-eps}.
  Suppose some $u$ satisfies $d(\conv(U_R),u) \leq \epsilon$ and $d(\conv(U_{R'}),u) \leq \epsilon$ for $R,R' \in \mathcal{S}$.
  Then $R \cap R' \neq \emptyset$, i.e. they have some report in common.
\end{lemma}
\begin{proof}
  We prove the contrapositive.
  Suppose $R \cap R' = \emptyset$.
  Suppose $d(\conv(U_r),u) \leq \epsilon$.
  By Lemma \ref{lemma:conv-R-min-eps}, we have that for ...

  \bo{Hmm -- need to rule out cases where they pass through each other, like the center of the squares in abstain loss R3.}
\end{proof}

@@

\end{proof}

>>>>

%\begin{lemma} \label{lemma:U-close-intersect}
%  Let $\epsilon$ be given by Lemma \ref{lemma:conv-R-min-eps}.
%  Suppose some $u$ satisfies $d(\conv(U_R),u) \leq \epsilon$ and $d(\conv(U_{R'}),u) \leq \epsilon$ for $R,R' \in \mathcal{S}$.
%  Then $R \cap R' \neq \emptyset$, i.e. they have some report in common.
%\end{lemma}
%\begin{proof}
%  We prove the contrapositive.
%  Suppose $R \cap R' = \emptyset$.
%  Suppose $d(\conv(U_r),u) \leq \epsilon$.
%  By Lemma \ref{lemma:conv-R-min-eps}, we have that for ...
%
%  \bo{Hmm -- need to rule out cases where they pass through each other, like the center of the squares in abstain loss R3.}
%\end{proof}

@@

Finally, we must show that $\psi$ is a separated, calibrated link.
\bo{...}
\end{proof}
